First Attempt at a Comparison Matrix

### 2015-09-21 early-analysis/001-test-compare-codes.Rmd
Move early analyses into separate folder

```{r}
codes_all_names <- str_extract(names(codes_all_grams), "\\w+")
comparison_of_all_codes <- outer_for_lists(codes_all_grams, codes_all_grams, compare_codes_by_shared_ngrams)
colnames(comparison_of_all_codes) <- codes_all_names
rownames(comparison_of_all_codes) <- codes_all_names
print(comparison_of_all_codes)
```

>>>>

```{r}
codes_all_names <- str_extract(names(codes_all_grams), "\\w+")
comparison_of_all_codes <- outer_for_lists(codes_all_grams, codes_all_grams, compare_codes_by_shared_ngrams)
colnames(comparison_of_all_codes) <- codes_all_names
rownames(comparison_of_all_codes) <- codes_all_names

# Normalize comparison of all codes to percentages
comparison_of_all_codes <- round(comparison_of_all_codes * 100, digits = 1)
print(comparison_of_all_codes)
```
